CDSR Human Data/Modelling Paper

### 2013-08-20 code/scenarios/cdsr/trunk/papers/ACS2013/main.tex
JK: added overview description of trial analysis

\section{Introduction - KLENK}

\section{Context-Dependent Spatial Regions - KLENK}

\subsection{Explanation of the basic idea}

@@

>>>>

\section{Introduction - KLENK} 
Natural communication between humans and cognitive systems requires both participants to communicate with spatial language.  Many spatial terms are defined not only be their geometry, but also their context.  That is, to understand this language requires considering the other objects and agents in the environment, as well as their configuration and functional roles.  We call such regions \textit{context-dependent spatial regions}(CDSRs).

We begin by discussing CDSRs with examples and two claims about these regions.  Next, we discuss desired properties of a cognitive system solution.  The contribution of this paper is a human study exploring our claims about CDSRs and an empirical exploration of current models and their shortcomings.  We close with a discussion of related and future work.

\section{Context-Dependent Spatial Regions - KLENK}
Consider the following regions: the front of a classroom (\ref{fig:classroom}), safety in military engagement (\ref{fig:safety}), or the geographical feature of a bottleneck (\ref{fig:bottleneck}).  To identify these regions, one must identify the physical boundaries (e.g., walls), the objects within the room and their functional use (e.g., desks oriented toward a whiteboard), and other agent's intentions and capabilities (e.g., enemy tanks can move and have a range of attack).  These regions exists at different levels of spatial resolution.  Consider a neighborhood in a city, whose boundaries expand and contract overtime with changes to the surrounding residents and businesses

@@

Method and Materials 
Trial 1
Trial 2
Trial 3

-----------------

Task 1: The participant draws a polygon denoting the region
Analysis of results:
(1) Do participants agree/understand-the-task? (validation of approach) + Should anyone be excluded?
Within the data for each trial,
-- For each participant, generate the intersection and union polygon of all the other participants
---- Generate N random points in the area of the full stimulus
---- For each of these N points check whether the participant's polygon and the [intersection/union] polygon both include it (agree++) or if one includes it and the other doesn't (disagree++)
---- Then we calculate a Cohen Kappa score as a measure of agreement between the participant and eveyone else. Note we need to calculate the chance of random agreement but we can do this as a function over the relative size of the participant's polygon in the total area of the stimulus and the relative size of the intersection/union polygon
(see http://en.wikipedia.org/wiki/Cohen%27s_kappa )

This process will result in for each trial a list of kappa scores for each participant indicating the extent to which they agree with everyone else. We are hoping for a high kappa score

(2) Does context matter?
I understand that all the rooms stimuli have the same extent.
So one way of evaluating whether context matters is to use the kapp score between the intersection/union polygon generated using all the response (less the excluded partitipants) for one trial and the equivalent polygon for another trial.
We are hoping for a low kappa score

-----------------

Task 2: The participant selected a point denoting the sweetspot of the region
Analysis of results:
(1) Do participants agree/understand-the-task? (validation of approach) + Should anyone be excluded?
Compare the variance across the subjects with the variance across a number of set of randomly generate points, where set size equals the number of participants, using the F distribution (http://www.ltcconline.net/greenl/courses/201/regression/comparingVariances.htm) where we are checking if the variance of the random points are greater than that of the participants.
We would hope that the variance of the subjects responses is lower than that of randomly generated points.
After the initial comparison with the random point sets we may exclude participants based on extreme variance.

(2) Does context matter?
Do the clusters of participants responses move?
- for each experimental stimulus compute the mean x and y location for the responses for that trial
- check whether the variance between the means of different stimuli responses is greater than the variance within each stimulus responses.

-----------------

Task 3: The participant grades a point with respect to membership of the region on a likert scale
I understand this experiment to be useful because (a) it asks the participants to evaluate (rather than generate cf task 1 and 2) (b) hopefully we can use it to reinforce our findings in task 1 and task 2
I think we need to be careful that the points we present to people for evaluation are reasonably well distributed so that we have a good chance of getting a variation across the responses
Assuming that there is a variation across the likert scores for a particular stimulus then check if their is a correlation between the scores and:
(a) inclusion in the intersection/union polygons from task 1 for the same stimulus
(b) distance from the mean sweet spot for that stimulus from task 2

-----------------
